Immutable Source-Mapped Abstract Syntax Tree: \\ A Design Pattern for Refactoring Engine APIs

### 2013-08-04 paper.tex
Modified options, layout for resubmission

% TODO: Version with [draft] is for draft mode only
%\documentclass[prodmode]{acmlarge}
\documentclass[draft]{acmlarge}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{url}
\usepackage{datetime} % for \today
\usepackage{listings} % for lstlisting environment
\usepackage{placeins} % for \FloatBarrier
\newcommand{\ttt}[1]{\texttt{#1}}
\newcommand{\code}[1]{\texttt{#1}}

@@

% Title portion
\title{Immutable Source-Mapped Abstract Syntax Tree: \\
A Design Pattern for Refactoring Engine APIs \\ \today}
\author{JEFFREY L.\ OVERBEY \affil{Auburn University}}

@@

\begin{wrapfigure}{R}{3in} % r is right, R is float right
% Original image is 4.624 x 10.651 in
\includegraphics[scale=0.65]{jdt-ast.eps}
%\caption{Visualization of the Eclipse Java Development Tools' abstract syntax
%tree for the following program: \\
%\ \\
%\centerline{\parbox{2in}{\ttt{\noindent public class Example \{ \\
%\hspace*{.2em} public int FIVE = 5; \\
%\}
%}}} \\
%\ \\
%The highlighted node---a \textit{VariableDeclarationFragment}---corresponds to
%the eight-character substring \ttt{FIVE = 5}, which begins with the 36th
%character in the source code.
%}
\caption{Visualization of an AST from Eclipse JDT.}
\label{fig:jdt-ast}
\end{wrapfigure}

@@

An \textit{abstract syntax tree} (AST) is a data structure that describes a
particular program in terms of this hierarchy.  Continuing with the Java
example, an AST typically describes the structure of a single Java source file.
The root node has three child nodes, corresponding to the three parts of a Java
source file: one child node describes the \ttt{package} statement, another
contains a list of \ttt{import} statements, and a third contains a list of type
declarations.  A type declaration has several child nodes, which describe
(among other things) its visibility, the name of the class or interface, and
the field/method declarations in its body.  A field declaration has child nodes
describing its visibility, type, and so forth.

@@

>>>>

% TODO: Version with [draft] is for draft mode only
% Also comment/uncomment \today in subtitle when in draft mode
\documentclass[prodmode]{acmlarge}
%\documentclass[draft]{acmlarge}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{url}
\usepackage{datetime} % for \today
\usepackage{listings} % for lstlisting environment
\usepackage{placeins} % for \FloatBarrier
\newcommand{\ttt}[1]{\texttt{#1}}
\newcommand{\code}[1]{\texttt{#1}}

@@

% Title portion
\title{Immutable Source-Mapped Abstract Syntax Tree: \\
A Design Pattern for Refactoring Engine APIs} % \\ \today}
\author{JEFFREY L.\ OVERBEY \affil{Auburn University}}

@@

@@

An \textit{abstract syntax tree} (AST) is a data structure that describes a
particular program in terms of this hierarchy.  Continuing with the Java
example, an AST typically describes the structure of a single Java source file.
The root node has three child nodes, corresponding to the three parts of a Java
source file: one child node describes the

\begin{wrapfigure}{r}{3in} % r is right, R is float right
% Original image is 4.624 x 10.651 in
\includegraphics[scale=0.62]{jdt-ast.eps}
%\caption{Visualization of the Eclipse Java Development Tools' abstract syntax
%tree for the following program: \\
%\ \\
%\centerline{\parbox{2in}{\ttt{\noindent public class Example \{ \\
%\hspace*{.2em} public int FIVE = 5; \\
%\}
%}}} \\
%\ \\
%The highlighted node---a \textit{VariableDeclarationFragment}---corresponds to
%the eight-character substring \ttt{FIVE = 5}, which begins with the 36th
%character in the source code.
%}
\caption{Visualization of an AST from Eclipse JDT.}
\label{fig:jdt-ast}
\end{wrapfigure}

\noindent
\ttt{package} statement, another
contains a list of \ttt{import} statements, and a third contains a list of type
declarations.  A type declaration has several child nodes, which describe
(among other things) its visibility, the name of the class or interface, and
the field/method declarations in its body.  A field declaration has child nodes
describing its visibility, type, and so forth.

@@

\FloatBarrier
